%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Cloud Infrastructure Management} % Job title
    {Capgemini} % Organization
    {Málaga, Spain} % Location
    {Jul. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built fully automated CI/CD pipelines on Jenkins for code deployment and manage services on Azure.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {DevOps Engineer} % Job title
    {Mr. Milú} % Organization
    {Madrid, Spain} % Location
    {Feb. 2022 - Jul 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained automated CI/CD pipelines for code deployment using gitlab and docker}
        \item {Provisioned an easily managable cloud infrastructure utilizing IaC tools like Ansible and Terraform.}
        \item {Built and deployed Docker containers for implementing Microservice Architecture from Monolithic Architecture}
        \item {Monitoring using Grafana, Prometheus.}
        \item {Succesfully created and maintaned automated tasks of gitlab using terraform resulting in the elimination of 70\% of manual\newline work and escalation of work efficiency}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Infrastructure Jr Analyst} % Job title
    {Avanade} % Organization
    {Málaga, Spain} % Location
    {Feb. 2021 - Feb 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deploy resources in Azure}
        \item {Succesfully created tools using Powershell that reduced manual work and increase the work efficiency.}
        \item {Monitoring with dynatrace.}
        \item {Administration Micorosoft 365 services.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
